---
title: "R Notebook"
output: html_notebook
---

```{r}
#Load data files
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)

library(plyr)
library(dplyr)
library(reshape)
library(ggplot2)
library(gtable)
library(lme4)
library(tidyverse)
library(simr)
library(lmerTest)
library(brms)
library(bootstrap)
library(ggpubr)
library(broom)    
library(entropy)

`%notin%` <- Negate(`%in%`)
```

# **Introduction**

This experiment studies the "satiation effect": the phenomenon whereby acceptability ratings increase throughout repeated exposure. It has been observed that different sentence types are variably sensitive to the satiation effect. This raises an important question: Why do certain sentence types satiate faster than others? (i.e. What factors modulate the rate of satiation? )

In this experiment, we aim to test the following hypotheses:

(1) Satiation rate is positively predicted by the representability of sentence structure (which can be measured by the inverse entropy of paraphrase meanings, or the confidence ratings)

(2) Satiation rate is negatively predicted by the availability of meaning-equivalent alternative forms (which can be measured by the entropy of paraphrase forms)

## **Experiment**

There are two experiment groups:

In **group A**, each trial consist of the following:

(1) Read a test sentence (one of the 11 conditions)

(2) Rate the acceptability of the sentence

(3) Rate their confidence in their interpretation

(4) Paraphrase

In **group B (N=34)**, each trial consist of the following:

(1) Read a test sentence (one of the 11 conditions)

(2) Rate the acceptability of the sentence

(3) Paraphrase

(4) Rate their confidence in their interpretation

Both groups did the same set of tasks, but in different order. We hope we can use this manipulation to figure out the best experiment design for the full study.

## Example Stimuli

**Adjunct island**: What did the student attend lecture because she read?

**S-V agreement error**: The clown were invited to the party by the host.

**Binding condition violation**: The bride thinks that the groom saw herself.

**CSC violation**: What did the horse eat apples and?

**Head directionality error**: The child surely the chocolate cake ate.

**LBC violation**: How many did you see cookies in the jar?

**Unlicensed NPI**: The spy saw anything yesterday.

**Subcategorization error**: The policeman relied for his instincts to catch the thief.

**Subject island**: What did a bottle of spill on the floor?

**Grammatical fillers**: The patient knew that the receptionist disliked him.

**Word-salad fillers**: Mechanic the that can power biofuel the does believe what ?

```{r}
#Read data file#
raw_data_path1 <- "../pilot_2a_ling145/pilot_2a_ling145-trials.csv"
data1<-read.csv(raw_data_path1)
non_native_1 = c(46,127,57,36,39,63,105,113,128)
#data1<- subset(data1, workerid %notin% non_native_1)

raw_data_path2 <- "../pilot_2b_ling145/pilot_2b_ling145-trials.csv"
data2<-read.csv(raw_data_path2)
non_native_2 = c(118, 81, 96, 104, 124,64,25,31,38,107,137,138)
#data2<- subset(data2, workerid %notin% non_native_2)
```

# Visualization

## Satiation plots

Let's first take a look at the overall satiation plot for group A

```{r}
data_no_practice1 = data1 %>% 
  filter(block_number != "practice") %>%
  mutate(block_number = as.numeric(block_number))

trial_means1 = data_no_practice1 %>%
  group_by(block_number,condition) %>%
  summarise(rating = mean(rating))

satiation_plot1 <- ggplot(data_no_practice1, aes(x=block_number, y=rating, color = condition, fill = condition)) + 
  geom_point(data=trial_means1,alpha=.9) + 
 # scale_color_manual(values=cbPalette) +
#  scale_fill_manual(values=cbPalette) +
  xlab("Presentation Order") +
  ylab("Acceptability rating")+
  geom_smooth(method=lm, aes(fill=condition))+theme_bw()

satiation_plot_faceted1 <- satiation_plot1 + facet_wrap(~condition, scales = "fixed")
satiation_plot_faceted1

```

Let's take a look at the same plot for group B:

```{r}
data_no_practice2 = data2 %>% 
  filter(block_number != "practice") %>%
  mutate(block_number = as.numeric(block_number))

trial_means2 = data_no_practice2 %>%
  group_by(block_number,condition) %>%
  summarise(rating = mean(rating))

satiation_plot2 <- ggplot(data_no_practice2, aes(x=block_number, y=rating, color = condition, fill = condition)) + 
  geom_point(data=trial_means1,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Presentation Order") +
  ylab("Acceptability rating")+
  geom_smooth(method=lm, aes(fill=condition))+theme_bw()
#satiation_plot2

satiation_plot_faceted2 <- satiation_plot2 + facet_wrap(~condition, scales = "fixed")
satiation_plot_faceted2


```

Here's a combined plot for the two groups:

```{r}
combined_data = rbind.fill(data_no_practice1,data_no_practice2)
trial_means = combined_data %>%
  group_by(block_number,condition) %>%
  summarise(rating = mean(rating))

satiation_plot <- ggplot(combined_data, aes(x=block_number, y=rating, color = condition, fill = condition)) + 
  geom_point(data=trial_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Presentation Order") +
  ylab("Acceptability rating")+
  geom_smooth(method=lm, aes(fill=condition))+theme_bw()
#satiation_plot2

satiation_plot_faceted <- satiation_plot + facet_wrap(~condition, scales = "fixed")
satiation_plot_faceted

```

## Confidence-Slope plots

Here's a plot of the satiation rate for each condition-participant combination against the confidence rating (Group A):

```{r}
slope_data1 = data_no_practice1 %>%
  group_by(workerid, condition)%>%
  do(tidy(lm(rating ~ block_number, data = .))) %>% 
  filter(term == "block_number") %>%    
  select(workerid, condition, estimate) 

merged_data1 <- data_no_practice1 %>%
  left_join(slope_data1, by = c("workerid", "condition"))

merged1_trial_means= merged_data1 %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate), meaning_confidence = mean(meaning_confidence))

confidence_slope_plot1 <- ggplot(merged_data1, aes(x=meaning_confidence, y=estimate, color = condition, fill = condition)) + 
#  geom_point(data=merged1_trial_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Confidence Rating") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
confidence_slope_plot1

```

Let's facet this by condition so that the plot is easier to read:

```{r}

confidence_slope_faceted1 <- confidence_slope_plot1 + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
confidence_slope_faceted1
```

Now Let's do the same for Group B:

```{r}
slope_data2 = data_no_practice2 %>%
  group_by(workerid, condition)%>%
  do(tidy(lm(rating ~ block_number, data = .))) %>% 
  filter(term == "block_number") %>%    
  select(workerid, condition, estimate) 

merged_data2 <- data_no_practice2 %>%
  left_join(slope_data2, by = c("workerid", "condition"))

merged2_trial_means= merged_data2 %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate), meaning_confidence = mean(meaning_confidence))

confidence_slope_plot2 <- ggplot(merged_data2, aes(x=meaning_confidence, y=estimate, color = condition, fill = condition)) + 
  #  geom_point(data=merged1_trial_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Confidence Rating") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
confidence_slope_plot2

```

Same as before, let's facet this by condition:

```{r}
confidence_slope_faceted2 <- confidence_slope_plot2 + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
confidence_slope_faceted2
```

Now, let's combined the two groups:

```{r}
slope_data = combined_data %>%
  group_by(workerid, condition)%>%

  do(tidy(lm(rating ~ block_number, data = .))) %>% 
  filter(term == "block_number") %>% 
  select(workerid, condition, estimate) 

merged_data <- combined_data %>%
  left_join(slope_data, by = c("workerid", "condition"))

merged_trial_means= merged_data %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate),meaning_confidence = mean(meaning_confidence))

confidence_slope_plot <- ggplot(merged_data, aes(x=meaning_confidence, y=estimate, color = condition, fill = condition)) + 
#  geom_point(data=merged1_trial_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Confidence Rating") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
confidence_slope_plot

```

Here's the faceted version of the combined plot:

```{r}
confidence_slope_faceted <- confidence_slope_plot + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
confidence_slope_faceted
```

### Entropy Plots

The meaning types are labeled by hand. Let's first plot Group A's meaning entropy (Hm) for each participant-condition combination against the satiation rates:

```{r}
data_no_fill1 <- subset(data_no_practice1, condition %notin% c("gram","ungram"))
entropy_results_1 <- data_no_fill1 %>%
  group_by(workerid, condition) %>%
  summarize(Hm = entropy(table(meaning_type)))

merged_data1_with_Hm <- merged_data1 %>%
  filter(condition %notin% c("gram","ungram"))%>%
  left_join(entropy_results_1, by = c("workerid", "condition"))


merged_Hm1_means= merged_data1_with_Hm %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate), Hm = mean(Hm))

Hm_plot_1 <- ggplot(merged_data1_with_Hm, aes(x=Hm, y=estimate, color = condition, fill = condition)) + 
  geom_point(data=merged_Hm1_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Hm") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
Hm_plot_1

```

Let's facet the above plot by condition:

```{r}

Hm_plot_1_faceted <- Hm_plot_1 + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Hm_plot_1_faceted
```

```{r}


```

Turning to Group B, let's create a entropy (for each condition-workerid pair) - satiation rate plot:

```{r}
data_no_fill2 <- subset(data_no_practice2, condition %notin% c("gram","ungram"))
entropy_results_2 <- data_no_fill2 %>%
  group_by(workerid, condition) %>%
  summarize(Hm = entropy(table(meaning_type)))

merged_data2_with_Hm <- merged_data2 %>%
  filter(condition %notin% c("gram","ungram"))%>%
  left_join(entropy_results_2, by = c("workerid", "condition"))


merged_Hm2_means= merged_data2_with_Hm %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate), Hm = mean(Hm))

Hm_plot_2 <- ggplot(merged_data2_with_Hm, aes(x=Hm, y=estimate, color = condition, fill = condition)) + 
  geom_point(data=merged_Hm2_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Hm") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
Hm_plot_2
```

This is too messy. Let's facet by condition:

```{r}
Hm_plot_2_faceted <- Hm_plot_2 + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Hm_plot_2_faceted
```

```{r}

```

Collapsing the two groups:

```{r}


merged_data_with_Hm <- rbind.fill(merged_data1_with_Hm,merged_data2_with_Hm)

merged_Hm_means= merged_data_with_Hm %>%
  group_by(workerid, condition)%>%
  summarise(estimate = mean(estimate), Hm = mean(Hm))

Hm_plot <- ggplot(merged_data_with_Hm, aes(x=Hm, y=estimate, color = condition, fill = condition)) + 
  geom_point(data=merged_Hm_means,alpha=.9) + 
  # scale_color_manual(values=cbPalette) +
  #  scale_fill_manual(values=cbPalette) +
  xlab("Hm") +
  ylab("Satiation Rate")+
  geom_smooth(method=lm)+theme_bw()
Hm_plot
```

Here's the merged plot faceted by condition:

```{r}
Hm_plot_faceted <- Hm_plot + facet_wrap(~condition, scales = "fixed")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Hm_plot_faceted
```

# Analysis

Which conditions satiated?

```{r}
combined_data$condition <- factor(combined_data$condition)
combined_data$condition <- relevel(combined_data$condition, ref = "gram")


satiation_model <- lmer(rating ~ block_number*condition + 
                          (1+block_number|workerid) , data = combined_data)
summary(satiation_model)
```

Does confidence rating predict satiation rate?

```{r}
merged_trial_means$condition <- factor(merged_trial_means$condition)
merged_trial_means$condition <- relevel(merged_trial_means$condition, ref = "subj_island")



conf_model <- lmer(estimate ~ meaning_confidence*condition + (1+meaning_confidence|workerid) , data = merged_trial_means)
summary(conf_model)
```

Does entropy predict satiation rate?

```{r}
merged_Hm_means$condition <- factor(merged_Hm_means$condition)
merged_Hm_means$condition <- relevel(merged_Hm_means$condition, ref = "subj_island")

Hm_model <- lmer(estimate ~ Hm*condition + (1+Hm|workerid) , data = merged_Hm_means)
summary(Hm_model)
```
